\name: Combining Bottom-up and top-down approaches through graph learning over interaction networks for drug-target-interaction prediction

### 2021-01-30 paper/main.tex
updated microAUC part

\subsubsection{Graph convolutional layers}
These molecular and ontology based sub-models were added to a larger
graph convolutional model, based on the protein-protein interaction
(PPI) graph. The PPI dataset is represented by a graph $G=(V,E)$,
where each protein is represented by a vertex $v\in V$, and each edge
$e\in E\subseteq V\times V$ symbolizes an interaction between two
proteins. Additionally, we introduce mapping
$x:V\rightarrow\mathbb{R}^{d}$ projecting each vertex $v$ to its node
feature $x_v = x(v)$, where $d$ denotes the dimensionality of the node
features.

@@

Note that drugs and proteins can be interchanged in this formulation, which we will denote with $MicroAUC_p$ and $MicroAUC_d$, respectively. As we want to evaluate the models performance to find all suitable drugs for each protein individually, \textit{$MicroAUC_p$} seems to be more reasonable in comparison to both $MicroAUC_d$ and $AUROC$ with respect to the previously proposed protein split cross-validation. Furthermore,

\subsection{Baseline model}
Our aim is to develop and evaluate a computational model to predict
drug--target interactions. Specifically, given a protein, we are
interested in identifying the drugs that may target the protein; this
scenario is motivated by the need to identify drugs that can target a

@@

Before introducing the core of our eventual model, we propose a suitable naive baseline model in order to analyze and understand the existing approaches and this novel method for drug target interaction prediction. For given lists $D, P$ of drugs and proteins, respectively, and a set of known interactions $Int := \{(d_i, p_i) \}$, we construct an interaction matrix $M_{int}\in\{0,1\}^{|D|\times|P|}$ with 
\begin{equation*}
	M_{ij} = \begin{cases}
		1 & \text{if } (d_i, p_j)\in Int\\
		0 & otherwise
	\end{cases}
\end{equation*}
describing for all drug--protein whether there is a known interaction or not. We now rank all proteins $p_j\in P$ descending by their number of drug interactors, characterized by 
\begin{equation*}
	f: P \rightarrow \mathbb{N} \text{ with } f:p_j \mapsto \sum_{i=0}^{|D|}M_{ij}
\end{equation*}
by summing over the columns of $M_{ij}$ and ranking these sums.
We now finish our baseline predictor $P_k$ by predicting all drugs to interact with the top $k$ targets, denoted by $TopK(P)$ w.r.t. $M_{ij}$ from the previously introduced ranking, formalized by

>>>>

1
\subsubsection{Graph convolutional layers}
These molecular and ontology based sub-models were added to a larger
graph convolutional model, based on the protein-protein interaction
(PPI) graph. The PPI dataset is represented by a graph $G=(V,E)$,
where each protein is represented by a vertex $v\in V$, and each edge
$e\in E\subseteq V\times V$ symbolizes an interaction between two
proteins. Additionally, we introduce mapping
$x:V\rightarrow\mathbb{R}^{d}$ projecting each vertex $v$ to its node
feature $x_v = x(v)$, where $d$ denotes the dimensionality of the node
features.

@@

Note that drugs and proteins can be interchanged in this formulation, which we will denote with $MicroAUC_p$ and $MicroAUC_d$, respectively. Note further that both are applicable to all three kinds of splitting schemes, but $MicroAUC_p$ and $MicroAUC_d$ are only plausible for protein split and drug split, respectively. As we want to evaluate the models performance to find all suitable drugs for each protein individually, \textit{$MicroAUC_p$} seems to be more reasonable in comparison to both $MicroAUC_d$ and $AUROC$ with respect to the previously proposed protein split cross-validation.

Our aim is to develop and evaluate a computational model to predict
drug--target interactions. Specifically, given a protein, we are
interested in identifying the drugs that may target the protein; this
scenario is motivated by the need to identify drugs that can target a

@@

\subsection{Baseline model}
Before introducing the core of our eventual model, we propose a suitable naive baseline model in order to analyze and understand the existing approaches and this novel method for drug target interaction prediction. For given lists $D, P$ of drugs and proteins, respectively, and a set of known interactions $Int := \{(d_i, p_i) \}$, we construct an interaction matrix $M_{int}\in\{0,1\}^{|D|\times|P|}$ with 
\begin{equation*}
	M_{ij} = \begin{cases}
		1 & \text{if } (d_i, p_j)\in Int\\
		0 & otherwise
	\end{cases}
\end{equation*}
describing for all drug--protein whether there is a known interaction or not. We now rank all proteins $p_j\in P$ descending by their number of drug interactors, characterized by 
\begin{equation*}
	f: P \rightarrow \mathbb{N} \text{ with } f:p_j \mapsto \sum_{i=0}^{|D|}M_{ij}
\end{equation*}
by summing over the columns of $M_{ij}$ and ranking these sums.
We now finish our baseline predictor $P_k$ by predicting all drugs to interact with the top $k$ targets, denoted by $TopK(P)$ w.r.t. $M_{ij}$ from the previously introduced ranking, formalized by
